---
title: "SRT411_A0"
author: "Winson Ruan"
date: "February 15, 2019"
output: pdf_document
---
---
title: "srt411A0"
author: "Winson Ruan"
date: "February 15, 2019"
output: pdf_document
---
This assignment is discussing on using R Studio, plotting a data graph on the application. This assignment provides a lesson on the advantages of R and idea of how to use the programming with the explanation. 

Document:https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#ToDo 1 Calculator
```{r}
((2019-2012)/(2019-1992))*100
```
#ToDo 2 Variables
```{r}
school = 2019-2012
life = 2019-1992
(school/life)*100
```
#ToDo 3 Functions
```{r}
c=c(4,5,8,11)
mean(x=c)
```
#ToDo 4 Plots
```{r}
x=rnorm(100)
plot(x)
```
#ToDo 5 Help
```{r}
help(sqrt)
```

#ToDo 6 Scripts
```{r}
source("todo6.R")
```
#ToDo 7 Matrices
```{r}
P=seq(from=31,to=60,by=1)
Q=matrix(data=P,ncol=5)
Q
```
#ToDo 8 Data Frames
```{r}
source("todo8.R")
plot(t)
```
#ToDo 9 Graphics
```{r}
source("todo9.R")
```
#ToDo 10 Reading and Writing data
```{r}
source("todo10.R")
todo10
```
#ToDo 11 Notavailable Data
```{r}
mean(x=sqrt(rnorm(100)))
```
#ToDo 12 Dates
```{r}
date=strptime(c("20190210","20191206","20190827"),format="%Y%m%d")
date
present=c(0,25,5)
present
plot(x=date,y=present)
```
#ToDo 13 For-Loop
```{r}
source("todo13.R")
np13
```
#ToDo 14 Writing your own function
```{r}
source("todo14.R")
todo14(arg1=1,arg2=100)

```
#ToDo 15 Footnote
```{r}
source("todo15.R")
todo15
```
